---
title: "App Rating Analysis using Generalized Logistic Regression"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(plyr)
library(corrplot)
source("modelling.R")
```

## Introduction

Multiple factors affect how a smartphone app is perceived by the user community, from the price tag to which category the app falls in. Different categories of apps can have different demographics of users and different rating and reviewing habits. If a developer team wants to build an app analysing the currently available apps can help in determining where they can find the most success.

Our goal is to find the relationships between the rating of an app and its number of installs, the app's price tag and the number of reviews. These are rather indirect variables that could be correleted to the rating of the application. We are interested in finding out how important these features are for predicting the rating and whether we can find any significant difference in the importance of the features.

We have used Generalized Logistic Regression as our model for the rating. The rating is divided into three categories - High, Medimum and Low - which correspond to rating values of (r >= 4.5), (4.5> r >= 3.5) and (3.5 > r) respectively. The categorisation is not uniform over the range of the ratings, but from our own experience, people don't perceive the ratings uniformly either. We perform one vs all logistic regression for all of these categories. Then we try to interpret the parameters.

Note: The dataset has more features, we had originally planned to use them in our analysis. But we had to limit our scope to fewer variables due to time and computational constraints.

## EDA and Preprocessing
The number of installs and price of the app are given as strings that cannot be directly converted into numbers. So we wrote functions to process and properly convert them into numerical data. The number of installs are still not strictly numerical, since the data we received had categories like "100+", "10,000+" them. We had to remove the dollar symbol for converting the price. Then we converted the ratings into categories as mentioned in the introduction.

| High     | Medium         | Low     |
|:--------:|:--------------:|:-------:|
| r >= 4.5 | 4.5 > r >= 3.5 | 3.5 > r |

Finally we dropped the extra features.

```{r load_data}
mydata <- load_data("data/Google-Playstore-32K.csv")
mydata["Rating"] <- 3 * mydata["Rating_high"] + 2 * mydata["Rating_med"] + 1 * mydata["Rating_low"]
mydata["Rating"] <- as.factor(mydata$Rating)
```

### Few observations in the data
```{r eda1}
print(head(mydata))
```

### Summary
```{r eda2}
summary(mydata)
```

### Rating bar plot
```{r rating_bar}
plt <- ggplot(mydata)
plt + geom_bar(aes(Rating), fill="#0066ff")
```

### Histogram of prices
```{r price_histogram, warning=FALSE}
plt <- ggplot(mydata)
plt + geom_histogram(aes(Price, fill=Rating), binwidth = 1) + xlim(-1, 10)
```

### Histogram of number of installs
```{r installs_histogram}
plt <- ggplot(mydata[mydata$Installs <= 1e6, ])
plt + geom_histogram(aes(Installs, fill=Rating), bins=20)
```

### Histogram of number of reviews
```{r reviews_histogram}
plt <- ggplot(mydata[mydata$Reviews < 1e4, ])
plt + geom_histogram(aes(Reviews, fill=Rating), bins=50)
```

### Distibutions of features

#### Reviews
```{r reviews_box}
plt <- ggplot(mydata)
plt + geom_boxplot(aes(x=Rating, y=Reviews), color="#0066ff") + scale_y_continuous(trans = "log10")
```

#### Correlation plot
```{r correlation}
M <- cor(mydata[,c("Reviews", "Installs", "Price")])
print(M)
```

```{r correlation_plot}
col1 <- colorRampPalette(c("#888888", "#880000"))
corrplot(M, method="number", type="upper", col=col1(4))
```
